Spin canonical rings of log stacky curves

### 2015-07-10 surfaces-write-up/surface-write-up.tex

\noindent
has a minimal presentation consisting of the $\sum_{i = 0}^{r}
{{m + i} \choose {i}}$ generators $\frac{u^d x_{\vec{v}}}{x_k^{c_i}}$
where $\vec{v} \in \bz_{\geq 0}^{m + 1}$ such that $\sum_{j = 0}^{m}
v_j = c_i$ and $z$ relations of the form
\[
	x_{\vec{u}} x_{\vec{v}} = x_{\vec{w}} x_{\vec{z}}
\]

\noindent
when $\sum_{i = 0}^{m + 1} u_i + v_i = \sum_{i = 0}^{m + 1} w_i + z_i$
\todo{fix this condition to make it right}
or of the form

\[
	x_{\vec{u}} x_{\vec{v}} = x_{\vec{w}} x_{\vec{z}}
\]

@@

\begin{proof}

>>>>

\noindent
has a minimal presentation consisting of the $\sum_{i = 0}^{r}
{{m + i} \choose {i}}$ generators $f_{\vec{v}} := \frac{u^{d_i}
x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$
such that $\sum_{j = 0}^{m} v_j = c_i$ and $z$ \todo{how many?}
relations of the form
\[
	x^{\vec{u}} x^{\vec{v}} = x^{\vec{w}} x^{\vec{z}}
\]

@@

\begin{proof}
We know $f_0$ is a minimal generator in degree $1$. If $x^{\vec{v}}$
were not minimal for $\deg \vec{v} = c_i > 0$ for some $i > 0$, then
$f_{\vec{v}} = f_{\vec{w}} f_{\vec{z}}$ for some $f_{\vec{w}},
f_{\vec{z}} \in R_D$ with $\deg \vec{w}, \deg \vec{z} < \deg \vec{v}$.
\end{proof}
